Global Deaths Due to Air Pollution

### 2022-05-11 Final Report.Rmd

---
title: "Final Report"
author: "Alison Cheek & Elizabeth Bekele"
date: '2022-05-10'
output: html_document
---
In our initial discussion over choosing a topic for our project, we narrowed it down to environmental-related data because we were interested in seeing possible trends over time and the vast quantity of environmental data that is available helped pique our curiosity.

>>>>

---
title: "Final Report: Air Pollution Deaths"
author: "Alison Cheek & Elizabeth Bekele"
date: '2022-05-10'
output: html_document
---
In our initial discussion over choosing a topic for our project, we narrowed it down to environmental-related data because we were interested in seeing possible trends over time and the vast quantity of environmental data that is available helped pique our curiosity.

### 2022-05-11 population_data.Rmd

high_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('United States', 'Brazil', 'Nigeria', 'Germany', 'Pakistan', 'Australia')) %>% 
  group_by(Year)

@@

low_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('Canada', 'Chile', 'Malawi', 'Serbia', 'Sri Lanka', 'New Zealand'))%>% 
  group_by(Year)

@@

head(world_pop)

>>>>

#Let's compare the first decade 1996-2006 with second decade 2007-2017 
high_pop_countries <- world_pop %>% 
  filter(Year > 1996 & Country.Name %in% c('United States', 'Brazil', 'Nigeria', 'Germany', 'Pakistan', 'Australia')) %>% 
  group_by(Year)

@@

low_pop_countries <- world_pop %>% 
  filter(Year > 1996 & Country.Name %in% c('Canada', 'Chile', 'Malawi', 'Serbia', 'Sri Lanka', 'New Zealand'))%>% 
  group_by(Year)

@@

#General overview of data 
head(world_pop, 12)
